Marlowe: implementing and analysing financial contracts on blockchain

### 2020-03-10 papers/marlowe2019/paper.tex
Adjust images

% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{IOHK, Hong Kong, 
\email{alexander.nemish@iohk.io, pablo.lamela@iohk.io, simon.thompson@iohk.io,~david.smith@tweag.io},  \and
School of Computing, University of Kent, UK, 
\email{s.j.thompson@kent.ac.uk}}
%
\maketitle              % typeset the header of the contribution

@@

\begin{wrapfigure}[9]{l}{0.25\textwidth}
    %\vspace*{-0.28in}
    \includegraphics[width=0.25\textwidth]{hole_options.png}
\end{wrapfigure}

@@

\begin{wrapfigure}[6]{l}{0.25\textwidth}
    \vspace*{-0.25in}
    \includegraphics[scale=0.2]{hole_options_2.png}
\end{wrapfigure}
A complete contract can be written in this guided way with the user needing only to fill in strings and numbers by hand. This approach to writing holes in your code and ``asking'' the compiler what you could put in there is easy to implement in a DSL because there are very limited options, however is is also becoming popular with more complex languages such as Haskell and Idris.

@@

\begin{wrapfigure}[5]{l}{0.5\textwidth}
    \vspace*{-0.2in}
    \includegraphics[scale=0.15]{input_composer.png}
\end{wrapfigure}

\noindent
The user can then choose to add this action to a transaction being prepared. Once the action is added other inputs become possible; these are displayed in the input composer, and again they can be added to the transaction being composed. In this way, multiple %actions can be added to a transaction before it is applied.

\begin{wrapfigure}[5]{l}{0.5\textwidth}
    \vspace*{-0.2in}
    \includegraphics[scale=0.15]{tx_composer.png}
\end{wrapfigure}

\noindent
actions can be added to a transaction before it is applied.
A user can then apply this transaction and in the example above this would result in the state pane showing a single payment and in addition the contract in the Marlowe editor will have been reduced to \lstinline{Close}.

>>>>

% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{IOHK, Hong Kong, 
\email{alexander.nemish@iohk.io, pablo.lamela@iohk.io, simon.thompson@iohk.io,~david.smith@tweag.io}  \and
School of Computing, University of Kent, UK, 
\email{s.j.thompson@kent.ac.uk}}
%
\maketitle              % typeset the header of the contribution

@@

\begin{wrapfigure}[9]{l}{0.25\textwidth}
    \vspace*{-0.24in}
    \includegraphics[width=0.25\textwidth]{hole_options.png}
\end{wrapfigure}

@@

\begin{wrapfigure}[5]{l}{0.20\textwidth}
%    \vspace*{-0.25in}
    \includegraphics[scale=0.18]{hole_options_2.png}
\end{wrapfigure}
A complete contract can be written in this guided way with the user needing only to fill in strings and numbers by hand. This approach to writing holes in your code and ``asking'' the compiler what you could put in there is easy to implement in a DSL because there are very limited options, however is is also becoming popular with more complex languages such as Haskell and Idris.

@@

\begin{wrapfigure}[4]{l}{0.47\textwidth}
    \vspace*{-0.28in}
    \includegraphics[scale=0.15]{input_composer.png}
\end{wrapfigure}

The user can then choose to add this action to a transaction being prepared. Once the action is added other inputs become possible; these are displayed in the input composer, and again they can be added to the transaction being composed. In this way, multiple %actions can be added to a transaction before it is applied.
actions can be added to a transaction before it is applied.

\begin{wrapfigure}[5]{l}{0.47\textwidth}
    \vspace*{-0.32in}
    \includegraphics[scale=0.15]{tx_composer.png}
\end{wrapfigure}

A user can then apply this transaction and in the example above this would result in the state pane showing a single payment and in addition the contract in the Marlowe editor will have been reduced to \lstinline{Close}.
